True versus apparent shapes of astrophysical bow shocks

### 2016-04-15 papers/Paper1/sec-application.tex
Week's changes in figures 2, 7 and respective sections

\begin{figure}
\includegraphics[width=\linewidth]{r-beta}
\caption{Bow shock shapes obtained with the \citep{Canto:1996} algebraic formalism using (\ref{eq:nprop}) to describe the proplyd wind density. The distance are normalized with $D$
to avoid dependency with this parameter.}
\label{fig:r-beta}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\linewidth]{r-beta}
\caption{Bow shock shapes obtained with the \citep{Canto:1996} algebraic formalism using (\ref{eq:nprop}) to describe the proplyd wind density. The distance are normalized with $D$
to avoid dependency with this parameter. In dashed lines, the \citep{Canto:1996} solution for two 
spherical, isotropic  interacting winds is shown, while in continuos lines we show the solution where the
weakest wind has a density distribution given by (\ref{eq:nprop})}
\label{fig:r-beta}
\end{figure}
